Predicting sales of newly published books

### 2015-09-10 paper.tex
updating table results (MLP)
resultados de las dos tablas completos
Problem section rewritten
I have put the second paragraph in front. Please @pacastillo check the second to see if it's still relevant. (I don't think so)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is published the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper we are tackling the problem of predicting total sales in order to %FERGU: The
                                %problem ON predicting, no? ¡gracias!  
% of predicting -  JJ
print the right amount of books, doing so even before the book has
reached shelves. 
In this paper, which works with several years of data on published books in
Spain, we first apply a data visualization and preprocessing strategy
in order to find
out what are the variables that have some impact on sales, and
then use standard data mining software to predict sales, and from them
deduce print-run, based on those variables. Our work focuses then in  discovering which
are the most relevant variables when predicting sales and is
eventually able to predict sales with remarkable accuracy. In fact,
this method has been validated by the company that provided the data 
and incorporated in a business intelligence tool for publishers,
since the obtained models provide guidance on the decision process of
publishing a book and do not require human intervention either for the operation or for
interpretation.
\end{abstract}

@@

%Sales forecasting in editorial industry is a very complex problem. 
        %hala, vuelta la burra al trigo - JJ
        %[Pedro] ea, lo quito   :)
There are several difficulties inherent to the new book sales forecasting, 
such as dealing with limited data, finding adequate forecasting methods, and 
selecting the best method to use \cite{ChingChin2010}.

The main issue of this paper is to compute forecasting of the sales for 
new unpublished-books, for which no historical data is available.
Thus, this paper faces the new book publishing problem using different 
prediction methods and using as inputs the historical sales data related 
to other yet published books, and some descriptive variables relative to 
the new unpublished-book.

@@

  %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
  % faltan AUN algunas ejecuciones de los de MLP (actualizo con los resultados últimos media+-stdev)
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
\hline
  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
\hline
  MLP     & 3595.24 $\pm$ 97.50 & 691.84 $\pm$ 82.71   & 1619.92 $\pm$ 91.67  & 108.74 $\pm$ 13.00   & 105.91 $\pm$ 5.99   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7} %FERGU: es normal que con menos variables tarde más? Sí, el uso de MATERIA y EDITORIAL hacen que el conjunto sea endiablado.
\end{table*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is published the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached shelves. 
In this paper, which works with several years of data on published books in
Spain, we first apply a data visualization and preprocessing strategy
in order to find
out what are the variables that have some impact on sales, and
then use standard data mining software to predict sales, and from them
deduce print-run, based on those variables. Our work focuses then in  discovering which
are the most relevant variables when predicting sales and is
eventually able to predict sales with remarkable accuracy. In fact,
this method has been validated by the company that provided the data 
and incorporated in a business intelligence tool for publishers,
since the obtained models provide guidance on the decision process of
publishing a book and do not require human intervention either for the operation or for
interpretation.
\end{abstract}

@@

The main issue of this paper is to forecast sales for 
unpublished books for which no historical data is available, just some
descriptive variables relative to the new book. In order to do that,
training data includes historical sales data for all books published
in Spain for several years, including those descriptive variables.

%Después de esto no sé si merece la pena dejar este párrafo.
Forecasting sales of new books is a problem with issues 
such as dealing with limited data, finding adequate forecasting methods and 
selecting the best method to use \cite{ChingChin2010}. % He cambiado
                                % esto, pero sigue sin decir
                                % absolutamente nada. "The problem"
                                % tiene que describir el problema: qué
                                % queremos hacer, qué tenemos - JJ

@@

  %[pedro] ya están todos los resultados de de tabla:results7 (MP5, LR, KNN, SVM, MLP)
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
\hline
  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
\hline
  MLP     & 3643.59 $\pm$ 72.40 & 696.92 $\pm$ 85.38 & 1609.37 $\pm$ 76.44  & 108.54 $\pm$ 13.34  & 105.96 $\pm$ 4.93   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7} %FERGU: es normal que con menos variables tarde más? Sí, el uso de MATERIA y EDITORIAL hacen que el conjunto sea endiablado.
\end{table*}
